A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit sample and data 1

    We use imaging data from the HSC internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the full depth in the Wide field. The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use $i$-band images for extracting surface brightness profiles. HSC $i$-band images are typically 3--4 mag deeper than SDSS (spell out here and reference ?????)  and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).

    In Paper~I, we select a sample of xxxxx(give number) massive galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. Within this redshift range, we have a large enough volume (xxx give the number here) to sample the galaxy mass function above $M-*>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ 
    kpc ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at 
    $z=0.3$ and 0.5), and we can safely ignore structural evolution over our redshift range (give time span in Gyr xxx).

>>>>

    We use imaging data from the HSC internal data release 
    \texttt{S15B}, which is very similar to the Public Data Release 1 
    (\citealt{HSC-DR1} and covers ${\sim} 110$ deg$^2$ in all five-band ($grizy$) to 
    the full depth in the Wide field. 
    The data are reduced by \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC (\citealt{HSC-PIPE}).
    The pixel scale of the reduced image is $0.168$\asec{}.
    We use $i$-band images for extracting surface brightness profiles. 
    HSC $i$-band images are typically 3--4 mag deeper than SDSS 
    (Sloan Digital Sky Survey; e.g. \citealt{SDSS-DR7, SDSS-DR8, SDSS-DR12})  
    and have superb seeing conditions (mean $i$-band seeing has FWHM$=0.6$\asec{}).

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5), and we can 
    safely ignore structural evolution over our redshift range ($\sim$1.5 Gyr of 
    time span).
